{mscstexta4r}

### 2016-06-14 README.Rmd
Remove build shields Combine textaDetectTopics tests

---
title: "{mscstexta4r}"
subtitle: "R Client for the Microsoft Cognitive Services Text Analytics REST API"
author: "Phil Ferriere"
date: "June 2016"
geometry: margin=0cm
output:
  html_document:
    self_contained: true
    highlight: tango
    keep_md: yes
    theme: cerulean
    toc: yes
    toc_depth: 4
    toc_float: yes
---
```{r echo=FALSE}
library("knitr")
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```
[![Build Status](https://api.travis-ci.org/philferriere/mscstexta4r.png)](https://travis-ci.org/philferriere/mscstexta4r)
[![codecov.io](https://codecov.io/github/philferriere/mscstexta4r/coverage.svg?branch=master)](https://codecov.io/github/philferriere/mscstexta4r?branch=master)
[![CRAN Version](http://www.r-pkg.org/badges/version/mscstexta4r)](https://cran.r-project.org/package=mscstexta4r)

>>>>

---
title: "{mscstexta4r}"
subtitle: "R Client for the Microsoft Cognitive Services Text Analytics REST API"
author: "Phil Ferriere"
date: "June 2016"
geometry: margin=0cm
output:
  html_document:
    self_contained: true
    highlight: tango
    keep_md: yes
    theme: cerulean
    toc: yes
    toc_depth: 4
    toc_float: yes
---
```{r echo=FALSE}
library("knitr")
knitr::opts_chunk$set(comment = "#>", collapse = TRUE)
```
